Insert the article title here

### 2018-05-25 writeup/manuscript.tex
Added citation to Amor et al 2017
Update manuscript.tex
Added AC and FG results, comments to intro

\begin{fmtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Anybody who has ever run a visual search experiment will be aware of the large differences from one participant to the next, and noting their existence is not new \cite{mackworth1948}. However, these differences are largely ignored and questions about their importance and stability remain relatively under explored. These differences could be due to several reasons: tiredness\cite{mackworth1948}, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}.

A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They found differences in visual search performance could be explained by whether observers used a scanning strategy, or simply fixated the centre of the stimulus and used peripheral vision.

@@

In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.

In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters. The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} \ldots. Even larger differences were found with the Split-Half Search Arrays \cite{nowakowsak2017} who aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies. They found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to match the performance of the stochastic searcher. Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.

@@

@@

The aim of the present study is to investigate the extent to which these differences are stable across different visual search paradigms. Are observers who are good at finding the target in the split-half search arrays also better in the ACVS task? Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms? As a secondary question, we will measure the test-retest reliability of the differences found in the split-half array paradigm.

@@

The ACVS was based on the task described in \cite{irons-leber2016}, with a few changes.

% These are the sizes of the boxes for each resolution, I'm not sure how best to incorporate this into the text though... here's a table for the meantime;
\begin{table*}
	\centering
	\small
	\begin{tabular}{cc|c}
	    Experiment	    &	Resolution	     & Size of stim \\
		\hline
		Adaptive Choice & $1024 \times 768$  & $\approx$$1.8^{\circ}$ \\
		Adaptive Choice & $1400 \times 1050$ & $\approx$$1.3^{\circ}$ \\
		Adaptive Choice & $1600 \times 1200$ & $\approx$$1.1^{\circ}$ \\
		Foraging        & $1024 \times 768$  & $\approx$$1^{\circ}$ \\
		Foraging        & $1400 \times 1050$ & $\approx$$0.7^{\circ}$ \\
		Foraging        & $1600 \times 1200$ & $\approx$$0.6^{\circ}$ \\
	\end{tabular}
	\caption{Size of stimuli for each experiment and screen resolution}
	\label{tab:Screen_Res}
\end{table*}

Each search display was composed of 54 small squares (size? What was viewing distance \& screen size?) arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed. Participants, were sat $\approx$47cm from the screen. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue. The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.

@@

In the feature foraging task, search displays contained 80 small circles (size), 20 red, 20 green, 20 blue  and 20 yellow. Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement. The location of item colours to grid locations was completely randomized.

@@

@@

@@

@@

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy. We now investigate whether there are correlations between paradigms: are individuals who are good at one visual search task good at another? We start by looking at simple reaction times (Figure \ref{fig:between_para_rt}). In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive. None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

Given the low correlations between reaction times, it seems unlikely that we will find that individuals who search efficiently and optimally in one paradigm will search well in another (the original motivation for our study). The analysis supports this hypothesis. For example, the correlation between the proportion of fixations to the heterogeneous side of the display in the split-half paradigm, and proportion of optimal targets found in the adaptive choice task is $r=-0.03$. Further results are presented in supplementary materials.

>>>>

\begin{fmtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%[TRIED A DIFFERENT, FEEL FREE TO CHANGE BACK
Anybody who has ever conducted a visual search experiment will be aware of the large differences from one participant to the next. These differences could be emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}. Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.

[MIGHT BE GOOD TO EXPLAIN HERE THAT THE EMPHASIS IS ON STRATEGY?] In the current study, we focus on one source of individual differences in visual search: strategy. By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability [NOT REALLY SURE HOW BEST TO SAY THAT, JUST THOUGHT IT MIGHT BE GOOD TO HAVE SOME OF DEFINITION OF VS STRATS??]. Recent studies have shown substantial variation in search strategies across individuals.

A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.

@@

% Memory stuff might be too left field for intro?
In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.

In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters. The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} examined strategies in the use of feature-based attention\cite{irons-leber2016,irons-leber2018} \ldots. Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to nearly optimal), and how often they changed search features. Even larger differences [haha we might argue with that, depending what you mean by larger] were found with the Split-Half Search Arrays \cite{nowakowsak2017} who aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies. They found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to match the performance of the stochastic searcher. Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.

@@

Mention \cite{amor2017}

@@

[MAYBE THERE SHOULD BE SOMETHING ELSE TO SET UP THE RESEARCH Q?] A common theme emerging from the studies in the observation that individual strategies vary in their degree of effectiveness or optimality [IF THAT IS EVEN A WORD]. However, each task taps into a different aspect of visual search behavior (feature-based attention, [spatial/fixation patterns??]). The aim of the present study is to investigate the extent to which these differences are stable across different visual search paradigms. Are observers who use the optimal strategy in the split-half search arrays also more optimal in the ACVS task? Are the super-foragers consistently better or worse than more typical searchers in the other two paradigms? As a secondary question, we will measure the test-retest reliability of the differences found in the split-half array paradigm.

@@

The ACVS was based on the task described in \cite{irons-leber2018}, Experiment 1.

% These are the sizes of the boxes for each resolution, I'm not sure how best to incorporate this into the text though... here's a table for the meantime;
% Thanks! Stim size is not critical for our experiment, so it doesn't matter too much if it's too complicated (just habit to have it in there :)
\begin{table*}
	\centering
	\small
	\begin{tabular}{cc|c}
	    Experiment	    &	Resolution	     & Size of stim \\
		\hline
		Adaptive Choice & $1024 \times 768$  & $\approx$$1.8^{\circ}$ \\
		Adaptive Choice & $1400 \times 1050$ & $\approx$$1.3^{\circ}$ \\
		Adaptive Choice & $1600 \times 1200$ & $\approx$$1.1^{\circ}$ \\
		Foraging        & $1024 \times 768$  & $\approx$$1^{\circ}$ \\
		Foraging        & $1400 \times 1050$ & $\approx$$0.7^{\circ}$ \\
		Foraging        & $1600 \times 1200$ & $\approx$$0.6^{\circ}$ \\
	\end{tabular}
	\caption{Size of stimuli for each experiment and screen resolution}
	\label{tab:Screen_Res}
\end{table*}

% Let me know if you want me to shift some of this into the Supp
Each search display was composed of 54 small squares arranged in three concentric rings around fixation, with 12, 18 and 24 items in the inner, middle and outer rings respectively. The same screen was used as in the Split-half Array Search, however, due to changes of screen resolution, the size of the squares changed. Participants, were sat $\approx$47cm from the screen. Of the 54 squares, 13 were red, 13 were blue, 14 were green and 14 were "variable". Variable distractors change colours from trial-to-trial according to a 24 trial cyclical pattern: the distractors would be red for 5 trials (called a "red plateau"), then across a period of 7 trials, they would change colour from almost red to magenta (at the fourth trial in the transition) to almost blue. The variable distractor would then be blue for 5 trials (blue plateau), and then transition back from almost blue through magenta to almost red.

@@

In the feature foraging task, search displays contained 80 small circles, 20 red, 20 green, 20 blue  and 20 yellow. Stimuli were arranged in a 10 x 8 grid, but the position of each item within the grid space was jittered to create a more random spatial arrangement. The location of item colours to grid locations was completely randomized.

@@

% Structure-wise, would it be easier for the reader to have methods and planned analyses nested under each task?

@@

The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure 3?). Figure 3 (? AC_OptCh_x_AllSw) shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$). Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber,2018}.

@@

The multiple-target foraging results were also in line previous findings \cite{kristjansson2014,johannesson2016}. As expected, run lengths were shorter for feature foraging ($M = 3.24$, $SD = 3.19$) than conjunction foraging ($M = 10.64$, $SD = 7.01$), $t(55) = 8.03$, $p < .001$ (PREFER DIFFERENT STATS HERE? CI [-9.25,-5.55]) suggesting more frequent foraging for multiple targets concurrently when those targets were defined by features than by conjunctions. However, both showed significant individual variation: Feature run length varied between 1.87 and 20, and conjunction run length varied between 1.00 and 19.67. Figure 4 (?) depicts run length across the trials separately for each individual. Twenty “super-searchers” were revealed, identified by short run lengths for both feature and conjunction targets [THAT NUMBER IS JUST BASED ON EYE-BALLING THE FIGURE, BUT WE COULD COME UP WITH SOME SORT OF PRECIOUS CUT OFF – WHAT DO YOU THINK?].

@@

The results above demonstrate that we have successfully replicated the previous findings around individual differences in visual search strategy. As an initial sweep, we look at overall performance in terms of RT (note that this can be influenced not only by strategy, but also by individuals’ abilities, such as their information-processing speed and their ability to ignore distractors). Are individuals who are fast on one visual search task fast on another? In all comparisons the correlations are weak, typically $0.27 < r <0.30$ but positive (Figure \ref{fig:between_para_rt}). None of these correlations are statistically significant ($p>0.05$). Even if we optimistically take all the data together as suggesting a robust correlation in reaction times from paradigm to paradigm, the upper bound of $r=0.30$ this correlation only accounts for at best $10\%$\footnote{i.e., $R^2 = 0.3^2 = 0.09$} an individual's performance.

@@

[I WONDER IF THIS SHOULD GO BEFORE THE RT CORRELATIONS? SINCE AS YOU SAY, THIS IS THE MAIN AIM OF THE PAPER. THEN RT CORRELATIONS COULD GO AS A SECONDARY AIM] Given the low correlations between reaction times, it seems unlikely that we will find that individuals who search efficiently and optimally in one paradigm will search well in another (the original motivation for our study) [I WOULD BE INCLINED NOT TO SAY THIS, BECAUSE IT SEEMS TO MINIMIZE THE PURPOSE OF LOOKING AT STRATEGY AT ALL. IE IT SUGGESTS THAT ALL OF THE VARIATION IN STRATEGY COULD BE ENCAPSULATED BY RT. BUT THERE ARE OTHER FACTORS THAT ALSO INFLUENCE RT]. The analysis supports this hypothesis. For example, the correlation between the proportion of fixations to the heterogeneous side of the display in the split-half paradigm, and proportion of optimal targets found in the adaptive choice task is $r=-0.03$. Further results are presented in supplementary materials.
